maASlin2

### 2019-12-05 scripts/10_genefamilies_KO_regroup.Rmd
update

```{r}
load('../data/kegg_lookup_tables.RData')
```

>>>>

### PCoA

```{r}
cts <- read_tsv('../data/humann2_res/humann2_final_out/humann2_genefamilies_KO_regroup_cpm_unstratified_reordered.tsv')

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  dplyr::rename(sampleid = Sampleid)

plot_BC_PCoA(cts, pheno, 'Toxicity')
```

### 2019-12-05 scripts/111_genefam_regroup_go.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GO.db)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GO.db)
source('~/pipeline/scripts/Computation/BC_distance_PCoA.R')
```

@@

### The PCoA of the GO regroup

```{r}
cts <- read_tsv('../data/humann2_res/humann2_final_out/humann2_genefamilies_uniref90_go_cpm_unstratified_reordered.tsv')

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  dplyr::rename(sampleid = Sampleid)

plot_BC_PCoA(cts, pheno, 'CR')
```

### 2019-12-05 scripts/112_genefam_eggnog.Rmd
update

```{bash}
# eggnog regroup
humann2_regroup_table             --input ../data/humann2_res/humann2_genefamilies.tsv              --groups uniref90_eggnog             --output ../data/humann2_res/humann2_genefamilies_uniref90_eggnog_regroup.tsv
# gropued 1+ more times:  ko 8%  eggnog 19.4% go 56.8%

@@

### Mapping the COG term to its name

>>>>

```{bash}
# eggnog regroup
humann2_regroup_table             --input ../data/humann2_res/humann2_genefamilies.tsv              --groups uniref90_eggnog             --output ../data/humann2_res/humann2_genefamilies_uniref90_eggnog_regroup.tsv
# gropued 1+ more times:  ko 8%  eggnog 19.4% go 56.8%  level4ec 9.8%

@@

### PCoA

```{r}
cts <- read_tsv('../data/humann2_res/humann2_final_out/humann2_genefamilies_uniref90_eggnog_regroup_cpm_unstratified_reordered.tsv')

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  dplyr::rename(sampleid = Sampleid)

plot_BC_PCoA(cts, pheno, 'CR')
```

### 2019-12-05 scripts/27_maASlin2.Rmd
update

>>>>

```{r}
# format the whole table column and keep the samples in the final cohort 33
have_sg <- read_csv('../data/baselinesforAngel10032019.csv') %>% 
  filter(shotgun_YN == 'yes') %>% 
  # removig 1943A cuz its low quality
  filter(sample_id != '1943A') %>% 
  ### FUCK THIS TABLE OF ../data/baselinesforAngel10032019.csv IS WRONG IN 161, it didn’t pass QC because not enough DNA material was present. SO WE DON'T HAVE THE SHOTGUN DATA.
  filter(!sample_id %in% c('161'))

phe_M <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 11252019 wo Censor .xlsx',
                    sheet = 5) %>% 
  rename_all(funs(str_replace_all(., ' \\(.+$','') %>% 
    str_replace_all(., ' ','_') %>% 
    str_replace(., ':|-','_'))) %>% 
  filter(is.na(Censor_reason)) %>% 
  filter(Baseline_Sample_ID %in% have_sg$sample_id)

```

```{r}
pheno <- phe_M %>% 
  dplyr::select(sampleid = Baseline_Sample_ID,
                CR, 
                ORR, 
                Toxicity, 
                Cytokine_Release_Syndrome,
                ICANS,
                Antibiotics_4_weeks_prior_to_CAR_T_cells,
                Antibiotics_4_weeks_post_CAR_T_cells,
                Disease_Class,
                Key__Patient_Disease_Status_at_CAR
                ) %>% 
  # change all the pheno vars to factors
  mutate_if(is.character, as.factor) %>% 
  column_to_rownames('sampleid') 
```
